Tables and Figures - Supplement A, B and C

### 2019-12-18 code/04_tables.rmd
General code cleanup

## Table 1
### Variation in observed effect sizes as a function of true effect size and measurement reliability.  
```{r effect-size-heterogeneity-table, cache = TRUE}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
ma <- c("I: $\\mu = 0.0$", "II: $\\mu = 0.3$", "III: $\\mu = 0.5$")

@@

#alternative inversed table 1
# table1b <- t(table1)[2:5,]
# studies <- c("Study 1: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "Study 2: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "Study 3: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)")
# table1b <- cbind(studies, table1b)
# rownames(table1b) <- NULL
# 
# table1b %>% knitr::kable(booktabs = T, col.names = c("Study and Measurement Error", "I: $\\mu = 0$", "II: $\\mu = .3$", "III: $\\mu = .5$"), escape = FALSE, digits = 2) %>% 
#   add_header_above(c(" " = 1, "Meta-Analysis" = 3)) %>% 
#   add_header_above(c(" " = 1, "Observed effect sizes" = 3)) %>% 
#   row_spec(3, hline_after = TRUE)
```
*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\mu$ when within study sample size is infinite. SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite within study sample sizes. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06

@@

sample_settings <- c("26/36 samples were primarily university students, 3 general population and 7 undescribed. 9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
                     "79/125 samples were collected in person (typically in labs), remainder online. Mean age in two rounds of data collection were 22.37 and 23.34 years.", #ML2
                     "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
                     "31/32 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR1
                     "22/23 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR2
                     "11/12 samples were undergraduate students mostly aged 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
                     "All samples consisted of in-lab undergraduate students", #RRR4
                     "All samples consisted of in-lab undergraduate students aged 18-25", #RRR5
               "All but one sample explicitly consisted of students and all took place in-lab. The last sample was recruited at university grounds.", #RRR6
               'All samples consisted of in-lab undergraduate students aged 18-34.', #RRR7
                     "All samples consisted of in-lab undergraduate students aged 18-25", #RRR8
               "All samples consisted of in-lab students aged 18-25",
               "All samples consisted of in-lab students aged 18-25")

@@

summary.table %>% knitr::kable(booktabs = TRUE,
                               digits = 0,
                               linesep = "\\addlinespace",
                               longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 7) %>%
  column_spec(2, width = "7em") %>% #specify width of paper column 
  column_spec(7, width = "16em") %>% 
  column_spec(8, width = "30em") %>% 
  landscape()
```
Note: For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. N = Participants used for primary analyses by original authors (i.e., after exclusions). RP = Replication Project, K (US) = no. primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06"

@@

#****************
#Results for "Heterogeneity Estimates and Confidence Intervals" section in paper

>>>>

## Table 1
### Variation in observed effect sizes as a function of true effect size and measurement reliability.  
```{r effect-size-heterogeneity-table, cache = TRUE}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
ma <- c("I: $\\rho_{xy} = 0.0$", "II: $\\rho_{xy} = 0.3$", "III: $\\rho_{xy} = 0.5$")

@@

#alternative inversed table 1
# table1b <- t(table1)[2:5,]
# studies <- c("Study 1: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "Study 2: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "Study 3: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)")
# table1b <- cbind(studies, table1b)
# rownames(table1b) <- NULL
# 
# table1b %>% knitr::kable(booktabs = T, col.names = c("Study and Measurement Error", "I: $\\rho_{xy} = 0$", "II: $\\rho_{xy} = .3$", "III: $\\rho_{xy} = .5$"), escape = FALSE, digits = 2) %>% 
#   add_header_above(c(" " = 1, "Meta-Analysis" = 3)) %>% 
#   add_header_above(c(" " = 1, "Observed effect sizes" = 3)) %>% 
#   row_spec(3, hline_after = TRUE)
```
*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\rho_{xy}$ when within study sample size is infinite. SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite within study sample sizes. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06

@@

sample_settings <- c("26/36 samples were primarily university students, 3 general population and 7 undescribed. 9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
                     "79/125 samples were collected in person (typically in labs), remainder online. Mean age in two rounds of data collection were 22.37 and 23.34 years.", #ML2
                     "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
                     "31/32 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR1
                     "22/23 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR2
                     "11/12 samples were undergraduate students mostly aged 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
                     "All samples consisted of in-lab undergraduate students", #RRR4
                     "All samples consisted of in-lab undergraduate students aged 18-25", #RRR5
               "All but one sample explicitly consisted of students and all took place in-lab. The last sample was recruited at university grounds.", #RRR6
               'All samples consisted of in-lab undergraduate students aged 18-34.', #RRR7
                     "All samples consisted of in-lab undergraduate students aged 18-25", #RRR8
               "All samples consisted of in-lab students aged 18-25", #RRR9
               "All samples consisted of in-lab students aged 18-25") #RRR10

@@

summary.table %>% knitr::kable(booktabs = TRUE,
                               digits = 0,
                               linesep = "\\addlinespace",
                               longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 7) %>%
  column_spec(2, width = "7em") %>% #specify width of paper column 
  column_spec(7, width = "16em") %>% 
  column_spec(8, width = "30em") %>% 
  landscape()
```
**Note:** For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. N = Participants used for primary analyses by original authors (i.e., after exclusions). RP = Replication Project, K (US) = no. primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06"

@@

#****************
#Results for "Heterogeneity Estimates and Confidence Intervals" section in paper----

### 2019-12-18 code/05_figures-and-correlations.rmd
General code cleanup

```{r cor_het_effect_size, results = "hide", cache=TRUE}

#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript

>>>>

```{r cor_het_effect_size, eval= FALSE}

#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript (not printed if .rmd is knit)

### 2019-12-18 code/06_Supplement-tables-figures.Rmd
General code cleanup

```{r, cache = FALSE}
a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2))) + geom_point() + ggtitle("SMD (untransformed)") +
  scale_x_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_y_continuous(name = "Tau")

@@

```{r, fig.width = 6, fig.asp = 1.3}

@@

_Figure S.1_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1. Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text). Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations.

@@

```{r}
knitr::kable(comparison, digits = 2, longtable = TRUE, booktabs = TRUE) %>% 
  add_header_above(c(" " = 1, "True effect size zero" = 4, "True effect size medium" = 4)) %>% 
  add_header_above(c(" " = 1, "Type I error rate and power for different heterogeneity levels" = 8))
```

@@

```{r, preprocessing}

@@

```{r, corr-table}

@@

```{r, no-anchoring-corr}
cors_anch <- round(cor(corr_data_no_anchoring), digits = 2)
cors_anch[upper.tri(cors_anch)] <- "" #make upper triangle empty in correlation matrix

>>>>

```{r a-plot, cache = FALSE}
a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2))) + geom_point() + ggtitle("SMD (untransformed)") +
  scale_x_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_y_continuous(name = "Tau")

@@

```{r combine-plots, fig.width = 6, fig.asp = 1.3}

@@

_Figure S1A_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1. Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text). Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations.

@@

```{r table-S1B}
knitr::kable(comparison, digits = 2, longtable = TRUE, booktabs = TRUE) %>% 
  add_header_above(c(" " = 1, "True effect size zero" = 4, "True effect size medium" = 4)) %>% 
  add_header_above(c(" " = 1, "Type I error rate and power for different heterogeneity levels" = 8))
```

@@

```{r preprocessing-supp-C}

@@

```{r table-S1C}

@@

```{r table-S2C-no-anchoring-SMD}
cors_anch <- round(cor(corr_data_no_anchoring), digits = 2)
cors_anch[upper.tri(cors_anch)] <- "" #make upper triangle empty in correlation matrix
